\documentclass[a4paper]{article}

\usepackage{amssymb}
\usepackage{color}
\usepackage{amstext}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{amsthm}
\usepackage{listings}

\usepackage[hmargin=3.5cm,vmargin=1.5cm]{geometry}

\begin{document}
\noindent Model v2:

\noindent Define $\delta:=$minimum degree.

\noindent Define $\Delta:=$maximum degree.

\noindent Define $n$ to be the number of vertices.

\begin{equation}
\label{eq:sym}
a_{i,j}=a_{j,i} \text{ } \forall i,j: i\neq j
\end{equation}

\begin{equation}
\label{eq:iizero}
a_{i,i}=0 \text{ } \forall i
\end{equation}

\begin{equation}
\label{eq:top}
\sum_{j=1}^{n}a_{1,j}=\delta
\end{equation}

\begin{equation}
\label{eq:twotoDelta}
\sum_{j=1}^{n}a_{i,j}=\Delta \text{ } 1<i\leq\Delta
\end{equation}

\begin{equation}
\label{eq:everythingelsesum}
\sum_{j=1}^{n}a_{i,j}=\delta \text{ } \Delta<i\leq n
\end{equation}

Constraint \ref{eq:sym} ensures that the adjacency matrix is symmetric.\\

Constraint \ref{eq:iizero} ensures the trace is 0.\\

Constraint \ref{eq:top} ensures the top row sums to $\delta$.\\

Constraint \ref{eq:twotoDelta} ensures the rows 2 through $\Delta$ sums to $\Delta$.\\

Constraint \ref{eq:everythingelsesum} ensures the rest of the rows sum to $\delta$.\\

As well as the above constraints the following initial conditions are given by algorithms as they are not simple to write in one line.

\textcolor{blue}{The following adds the 0 matrix around the trace where appropriate.}

\vspace{0.5em}
for $c=0 < \delta$ \\
\-\hspace{1.5cm}for $i=\Delta+1+c\delta < \Delta+\delta(c+1)$ \\
\-\hspace{3cm}for $j=i+1\leq\Delta+\delta(c+1)$ \\
\-\hspace{4.5cm}$a_{i,j}=0$

\vspace{0.5em}
\textcolor{blue}{The following adds the identity matrix where appropriate.}

\vspace{0.5em}
for $i=\Delta+1\leq\Delta+\delta$\\
\-\hspace{1.5cm}for $b=1<\delta$ \\
\-\hspace{3cm}$a_{i,j+(b-1)\delta}=1$

\vspace{0.5em}
\textcolor{blue}{The following sets the first row.}

\vspace{0.5em}
for $j=2\leq\Delta$\\
\-\hspace{1.5cm} $a_{1,j}=1$

\vspace{0.5em}
\textcolor{blue}{The following sets the rows 2 through $\Delta$ appropriately.}

\vspace{0.5em}
for $i=2\leq\Delta$\\
\-\hspace{1.5cm}for $j=1\leq\delta$\\
\-\hspace{3cm}$a_{i,j+(i-1)\delta+1}=1$

\vspace{0.5em}
\noindent Notes:
\begin{itemize}
\item don't need column sum because of symmetry of the row sum.
\item don't need triangle constraints hopefully because of further constraints to be added.
\item don't need square constraints hopefully because of further constraints to be added.
\end{itemize}
\end{document}
